### 2015-05-07 Workshop2015/camera-ready/incremental.tex
Nadia's version

In our context, data are provided by services deployed on different clouds. 
In the preivous   MOOC system example, several producers will supply equivalent content for a given period of time. 
They will be chosen with respect to the  preferences expressed by a consumer.

@@

The Abstract Inter-Cloud Layer (ICL) delivers the results to the  query. 
The ICL  first identifies a set of abstract functionalities  and associated services that fit the  query. These descriptions are stored in a service description registry.

@@

\begin{figure*}
\center{
\includegraphics[width=0.65\textwidth]{workflow.pdf}
\caption{SLA guided  data integration workflow.\label{fig:arch}}}
\end{figure*}

@@

Some of these measures ({cost/call, maxCall/day}) are static and explicitly specified by the service provider. 
In contrast, the other measures should be computed by monitoring the conversations between the service and the applications that contact it.  It is the case of service reputation that will determine the way personal user data will be anonymized (Constraint1).  Some measures will be instantiated depending on the context of  the service invoked within a multi-cloud environment. It is the case for constraint 2 expressed above:   user data access credentials should be calculated according to the policies adopted by the clouds  hosting  data services.
An \textit{agreed SLA} is given as an  XML document using the specification WSLA (Web service level agreement\footnote{\footnotesize http://www.research.ibm.com/people/a/akeller/\-Data/WSLASpecV1-20030128.pdf}).

@@

Let us suppose that for $Q_1$  the user is ready to pay a total cost of maximum  \$1; she requests that content providers be certified as experts (provenance) even if their data are not fresh; she requires to receive content  during  one week. Besides, she wishes to keep the content exchange private and she wants to order services by reputation. The maximum total cost will  also determine the kind of privacy preserving algorithms that will be applied.

>>>>

In our context, data are provided by services deployed on different clouds. 
In the previous   MOOC system example, several producers will supply equivalent content for a given period of time. 
They will be chosen with respect to the  preferences expressed by a consumer.

@@

The Abstract Inter-Cloud Layer (ICL) (see Figure~\ref{fig:arch} is responsible to deliver the results to the  query. 
The ICL  first identifies a set of abstract functionalities  and associated services that fit the  query. These descriptions are stored in a service description registry.

@@

\begin{figure*}
\center{
\includegraphics[width=0.66\textwidth]{workflow.pdf}
\caption{SLA guided  data integration workflow.\label{fig:arch}}}
\end{figure*}

@@

Some of these measures ({cost/call, maxCall/day}) are static and explicitly specified by the service provider. 
In contrast, the other measures should be computed by monitoring the conversations between the service and the applications that contact it.  It is the case of user privacy-preserving service that will determine the way personal user data will be anonymized (Constraint1).  Some measures will be instantiated depending on the context of  the service invoked within a multi-cloud environment. It is the case for constraint 2 expressed above:   user data access credentials should be calculated according to the policies adopted by the clouds  hosting  data services.
An \textit{agreed SLA} is given as an  XML document using the specification WSLA (Web service level agreement\footnote{\footnotesize http://www.research.ibm.com/people/a/akeller/\-Data/WSLASpecV1-20030128.pdf}).

@@

Let us suppose that for $Q_1$  the user is ready to pay a total cost of maximum  \$1; she requests that content providers be certified as experts (provenance) even if their data are not fresh; she requires to receive content  during  one week. Besides, she wishes to keep the content exchange private and she wants to order services by reputation. The maximum total cost will  also determine the kind of privacy preserving algorithms that should be applied.

### 2015-05-07 Workshop2015/camera-ready/introduction.tex
Nadia's version

To better understand our problem, consider a massive open online course system (MOOC) where users produce and consume content according to the geographic area and the expertise of participants. 
Producers are characterized according to their location, the type and topic of  content  they can provide, the access conditions (e.g. cost, inscription, or exchange unit), and the time window in which they can produce content. 
Consumers are characterized by their location, their interests  during a certain interval of time, the maximum total cost they are ready to pay consuming content, or the resources they are ready to provide in order to get the service, and QoS requirements such as availability and how critical it is to consume a given type of content. Both producers and consumers have subscriptions to different cloud providers for dealing with content storage, processing and exchange.
The MOOC  aims at being privacy respectful of the producers and consumers participating in courses.
 Providers  and consumers can ask to minimize the transfer of personal data  when they share/consume content.  According to the level of trust associated to data providers, the MOOC can use privacy preserving technics to let users share content anonymously  (Constraint1). Furthermore,  data providers can  also wish to give restricted data access credentials w.r.t. to their own, when their data are used  within  an integration process (Constraint 2).

@@

  The first step is to propose an architecture that integrates all services participating in a data integration process that copes QoS and SLA's of the services that participate in this process for computing a given query. 
  We have proposed such architecture in~\cite{BennaniGMV14}. Based on this architecture it is necessary to revisit  the integration phases  specification to include QoS and SLA. The objective being to  propose a new way of dealing with a data production and consumption process, considering SLA formalism and clauses -especially security concerns-  and heterogeneity among clouds. Therefore, this paper introduces a preliminary solution addressing SLA-guided data integration focusing  on query rewriting addressing security issues. We assume that data services publish Agreed-SLA that describe their  static and dynamic QoS measures in specific registries.  Thanks to an extended query rewriting process, a new kind of SLA is derived to match user preferences with low level agreed SLAs exported by services. The derived SLA allows to choose  services (w.r.t user requirements) that can contribute for answering a query. Once data services have been chosen, the integration process will be guided by an integration SLA, negotiated taking according to user requirements and inter-cloud contracts.

>>>>

To better understand our problem, consider a massive open online course system (MOOC) where users produce and consume content according to the geographic area and the expertise of participants. 
Producers are characterized according to their location, the type and topic of  content  they can provide, the access conditions (e.g. cost, inscription, or exchange unit), and the time window in which they can produce content. 
Consumers are characterized by their location, their interests  during a certain interval of time, the maximum total cost they are ready to pay consuming content, or the resources they are ready to provide in order to get the service, and QoS requirements such as availability and how critical it is to consume a given type of content. Both producers and consumers have subscriptions to different cloud providers for dealing with content storage, processing and exchange.
The MOOC  aims at being privacy respectful of the producers and consumers participating in courses.
 Providers  and consumers can ask to minimize the transfer of personal data  when they share/consume content.  According to the level of trust associated to data providers, the MOOC can use privacy preserving technics to let users share content anonymously  (Constraint1). Furthermore,  data providers can  also wish to give restricted data access credentials w.r.t. to their  trust level, when their data are used  within  an integration process (Constraint 2).

@@

  The first step is to propose an architecture that integrates all services participating in a data integration process that copes QoS and SLA's of the services that participate in this process for computing a given query. 
  We have proposed such architecture in~\cite{BennaniGMV14}. Based on this architecture it is necessary to revisit  the integration phases  specification to include QoS and SLA. The objective being to  propose a new way of dealing with a data production and consumption process, considering SLA formalism and clauses -especially security concerns-  and heterogeneity among clouds. Therefore, this paper introduces a preliminary solution addressing SLA-guided data integration focusing  on query rewriting addressing security issues. We assume that data services publish Agreed-SLA that describe their  static and dynamic QoS measures in specific registries.  Thanks to an extended query rewriting process, a new kind of SLA is derived to match user preferences with low level agreed SLAs exported by services. The derived SLA allows to choose  services (w.r.t user requirements) that can contribute for answering a query. Once data services have been chosen, the integration process will be guided by an integration SLA, negotiated according to user requirements and inter-cloud contracts.
